Code Overflow: \\ An empirical study of online code reuse

### 2016-08-17 latex/stackoverflow.tex

\subsection{Investigation of the largest unique 172 clone pairs}
In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations. However, only 10 of them appear in the new results using tool's agreement. Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement. With our 4 settings, we investigated the largest 172 clone pairs according to their average SLOC (larger than or equals to 15 SLOC). These clone pairs are pairs of Stackoverflow fragments and Java files from Qualitas projects that NEVER been looked at before in the previous investigation. The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files. The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:classification_breakdown}.

\begin{table}[H]
	\centering
	\caption{Classification results of 14 \textit{good} and 510 \textit{ok}-matches (including the subsumed \textit{good}-match pairs).}
	\label{tab:classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|}
		\hline 
		Classification & A & B & C & D & E & F & Total \\ 
		\hline 
		\multirow{2}{*}{\textit{good-match(0.7)}} & 1 & 2 & 2 & 2 & 7 & 0 & 14 \\ \cline{2-8}
		& 7.14\%	& 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
		\hline
		\multirow{2}{*}{\textit{ok-match(0.7)}} & 4 & 42 & 8 & 351 & 28 & 77 & 510 \\ \cline{2-8}
		& 0.78\%	& 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
		\hline
		\multirow{2}{*}{172 indv. pairs} & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\ \cline{2-8}
		& 9.88\% & 4.07\% & 1.74\% & 12.21\% & 2.91\% & 69.19\% & 100.00\%  \\ 
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Breakdowns of the biggest 172 individual clone pairs}
	\label{tab:classification_breakdown}
	\begin{tabular}{|l|r|r|r|r|r|r|r|}
		\hline 
		Classification & A & B & C & D & E & F & Total \\ 
		\hline 
		Simian$_{df}$ & 16 & 7 & 3 & 7 & 4 & 3 & 40 \\ 
		\hline
		Simian$_{fse13}$ & 1 & 0 & 0 & 1 & 0 & 53 & 55 \\
		\hline
		NiCad$_{df}$ & 0 & 0 & 0 & 13 & 0 & 22 & 35 \\
		\hline
		NiCad$_{fse13}$ & 0 & 0 & 0 & 0 & 1 & 41 & 42 \\
		\hline
		Total & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\
		\hline
	\end{tabular} 
\end{table}

>>>>

\subsection{Investigation of the largest unique 172 clone pairs}
In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations. However, only 10 of them appear in the new results using tool's agreement. Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement. With our 4 settings, we investigated the largest 172 clone pairs according to their average SLOC (larger than or equals to 15 SLOC). These clone pairs are pairs of Stackoverflow fragments and Java files from Qualitas projects that NEVER been looked at before in the previous investigation. The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files. The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:good_classification}.

\begin{table}[H]
	\centering
	\caption{Classification results of 1,406 \textit{good} and ??? \textit{ok}-matches (including the subsumed \textit{good}-match pairs).}
	\label{tab:classification}
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Classification & A & A' & B & C & D & E & F & Total \\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}} & 1 & 0 & 1 & 3 & 26 & 6 & 1,369 & 1,406 \\ \cline{2-8}
		%& 7.14\%	& & 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
		\hline
		\multirow{1}{*}{\textit{ok-match(0.7)}} &  & &  &  &  &  &  &  \\ \cline{2-8}
		%& 0.78\%	& & 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
		\hline
		\multirow{1}{*}{172 indv. pairs} &  & &  &  &  &  &  &  \\ \cline{2-8}
		%& 9.88\% & & 4.07\% & 1.74\% & 12.21\% & 2.91\% & 69.19\% & 100.00\%  \\ 
		\hline
	\end{tabular} 
\end{table}

\begin{table}[H]
	\centering
	\caption{Breakdown of each category A--F according to agreement}
	\label{tab:good_classification}
\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
	\hline 
	Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
	\hline
	Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
	Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
	Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
	Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
	\hline
	Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
	\hline
\end{tabular} 
\end{table}

%\begin{table}[H]
%	\centering
%	\caption{Breakdowns of the biggest 172 individual clone pairs}
%	\label{tab:classification_breakdown}
%	\begin{tabular}{|l|r|r|r|r|r|r|r|}
%		\hline 
%		Classification & A & B & C & D & E & F & Total \\ 
%		\hline 
%		Simian$_{df}$ & 16 & 7 & 3 & 7 & 4 & 3 & 40 \\ 
%		\hline
%		Simian$_{fse13}$ & 1 & 0 & 0 & 1 & 0 & 53 & 55 \\
%		\hline
%		NiCad$_{df}$ & 0 & 0 & 0 & 13 & 0 & 22 & 35 \\
%		\hline
%		NiCad$_{fse13}$ & 0 & 0 & 0 & 0 & 1 & 41 & 42 \\
%		\hline
%		Total & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\
%		\hline
%	\end{tabular} 
%\end{table}
